MC-based feasibility study of new sampling calorimeter for measuring the $\gamma$ incident angle

### 2022-01-24 paper.tex
updates

\begin{figure}[!hbt]
\includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}
\caption{ \textcolor{red}{plots should be updated} Schematic view of the sampling calorimeter. It consists of alternating lead plates and scintillator strips.  }
\label{fig:det_conf}
\end{figure}

@@

\begin{figure}[!hbt]
\includegraphics[width=0.89\textwidth]{figures/Fig1_reco_def.pdf}
\caption{\textcolor{red}{plots should be updated} The angular resolution for the varying AAA and the varying BBB. The best angular resolution is obtained with AAA=XXX and BBB=YYY.  }
\label{fig:par_scan}
\end{figure}

As the reconstruction of the incident angle depends on hyperparameters of the $\XGB$, which controls the details of training processes, dedicated tests to optimize the hyperparameter were executed. It is assumed that a set of hyperperameters providing the best angular resolution would be optimized. The test scans the evaluated angular resolution with different hyperparameters. Figure~\ref{fig:par_scan} shows the result of the test for AAA and BBB. The AAA works for *******, and the BBB works for *****. The AAA and BBB are determined to be XXX and YYY, respectively. Different tests determine the set of hyperparameters, which is shown in Tab~\ref{tab:XgbPar}.

\begin{table}[hbt!]
\centering
\caption{Hyperparameters of the $\XGB$}
\begin{tabular}{cccc}
\hline 
Parameter & Function & Default value & Used value \\ \hline 
N\_estimators & The number of decision trees & N.A. & 1000 \\  
Max. depth & Possible maximum depth of tree structure & 6 & 100 \\ 
Subsample & Fraction of total data used for a single decision & 1 & 1 \\ 
Learning rate & Step length for calculation & 0.3 & 0.08 \\ 
Gamma & Requirement on minimum loss function & 0 & 0 \\ 
\hline
\end{tabular}
\label{tab:XgbPar}
\end{table}

>>>>

\begin{figure}[!hbt]
\includegraphics[width=0.85\textwidth]{figures/Sec2/Prototype_samplingcal.pdf}
\caption{ \textcolor{red}{plots should be updated} Schematic view of the sampling calorimeter. It consists of 105 alternating lead plates and scintillator strips. Each scintillator layer consists of 35 scintillator strips. The cross section of each 1-mm-thick lead plate is 525 mm $\times$ 525 mm. The cross section of each 5-mm-tihck scintillator strip is 525 mm $\times$ 15 mm. }
\label{fig:det_conf}
\end{figure}

@@

\begin{figure}[!hbt]
\includegraphics[width=0.89\textwidth]{figures/optimization_plot.pdf}
\caption{The angular resolution for the varying N\_estimators and the varying Max. depth. The best angular resolution is obtained with N\_estimators=300 and Max. depth=100.  }
\label{fig:par_scan}
\end{figure}

As the reconstruction of the incident angle depends on hyperparameters of the $\XGB$, which controls the details of training processes, dedicated tests to optimize the hyperparameter were executed. It is assumed that a set of hyperperameters providing the best angular resolution would be optimized. The test scans the evaluated angular resolution with different hyperparameters. Figure~\ref{fig:par_scan} shows the result of the test for N\_estimators and Max. depth. N\_estimators defines allowed maximal number of decision trees, and the Max. depth defines complexity of the structure of decision trees. The N\_estimators and Max. depth are determined to be 300 and 100, respectively. Similar tests are applied to different hyperparameters, and definitive values for each hyperparameter are shown in Tab~\ref{tab:XgbPar}.

\begin{table}[hbt!]
\centering
\caption{Hyperparameters of the $\XGB$}
\begin{tabular}{cccc}
\hline 
Parameter & Function & Default value & Used value \\ \hline 
N\_estimators & The number of decision trees & N.A. & 300 \\  
Max. depth & Possible maximum depth of tree structure & 6 & 100 \\ 
Subsample & Fraction of total data used for a single decision & 1 & 0.8 \\ 
Learning rate & Step length for calculation & 0.3 & 0.02 \\ 
Gamma & Requirement on minimum loss function & 0 & 0 \\ 
\hline
\end{tabular}
\label{tab:XgbPar}
\end{table}
